---
title: "Nowcasting Package: how to use?"
author: "Guilherme Branco Gomes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package contains a collection of function to estimate forecasts for the near futures or the recent past, in other words nowcasting. The econometric framework is a model of state spaces with maney variables and commom components, the Dynamic Factor Model.
In this first version we focus on the problem when the variable of interest is a quarterly time series and the regressor are monthly time series.

## Dynamic Factor Model

This model can be specified in a space state representation:
$$X_t = C F_t + e_t$$
$$ F_{t} = \sum_{k=1}^p (A_{j}L^kF_t) + Bu_t$$
where:

* $X_t$ is a vector with $n$ observable series, $F_t$ is a vector with $r$ latent series called commom factors;
* $e_t$ is a vector of $n$ idiosyncratic component, u_t is a vector of $q$ commom shocks;
* $C$ is a $n \times r$ matrix, $A_j$ is a $r \times r$ matrix, $L$ is the lag operator, $B$ is a $r\times q$ matrix.

For more details about the specifications of this model see the survey (Stock and Watson 2011)


## Mixed Frequency

How treat mixed frequency, when we are interest in quarterly estimation using monthly variables.
Murasawa e Mariano 2003 approximation, bridge equation and EM

## Models

Little words about each method of estimation

### Two Stages - with quarterly factors

### Two Stages - with monthly factors

### Expected Maximization


## Data extraction and annalysis

BRGDP

```{r, echo=FALSE, results='asis'}
BRGDP<-nowcasting::BRGDP
datas<-zoo::as.Date(BRGDP)
df<-data.frame(nowcasting::BRGDP)
row.names(df)<-datas
knitr::kable(data.frame(df),row.names = T)
```

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
